\sc Building sex-specific synthetic lethality network in cancer - Temp Name

### 2023-07-26 sl_report_pmcrc/paper0904.tex
updates

>>>>

	The pre-filtered matrices were then normalized using the DESeq2 package in R \citep{love2014moderated}. RNA-seq data must be normalized in order to account for factors that prevent the direct comparison of expression measures. The DESeq2 R package employs a median of ratios normalization method to account for the inherent biases associated with RNA-seq data.
